Weakly Nonlinear MRI: Notes

### 2014-04-07 notes/mri_notes.tex
Fredholm alternative
Fredholm alternative+

>>>>

Some thoughts on the solvability conditions: \\

The solvability condition arises from the Fredholm alternative, which I looked up in Guenther \& Lee (1988). It states that if you have: \\

$M Y = F$ and $M^\dagger Z = G$ \\

And the corresponding homogenous equations, and if $M^\dagger Z = 0$ has a solution, then $M Y = F$ has a solution if and only if $\left<F \cdot Z \right> = 0$, where Z is the nontrivial solution to the adjoint homogenous equation. \\

In our case, we have: \\

$\mathcal{L}\mathbf{V_2} \, = \mathbf{N_2} - \widetilde{\mathcal{L}}_1 \partial_Z \mathbf{V_1}$ \\

Where $\widetilde{\mathcal{L}}_1 \partial_Z \mathbf{V_1}$ contains a term resonant with $e^{iQz}$. This is a secular term because it is a solution of the homogenous equation. \\
